---
title: "PhoCAssPaNS_O2Cell_dataAnalysis"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Scope

This file aims at determining the oxygen productivity of the microalgae CHlorella vulgaris NIES 227 according to light intensity measured as part of the study Scalable modelling of photosynthetic carbon assimilation and partition during
  nitrogen starvation for the microalga Chlorella vulgaris NIES 227.
  
The data collected in that study is loaded and then analysed as described in the manuscript and suplementary information of the associated study.

# Initialisation
## Setting path for data file

The path to read the file of data and import the results into the workspace is set below.

```{r set username, include=FALSE}
localPath <- getwd()
```

## Sourcing of functions 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

debugSource(paste(localPath,'/Auxiliary R functions/o2cell_prod_fun_kl_corrected.R',sep = ""), echo=TRUE)
```

# Data import

```{r cars}
general_path <- paste(localPath,'/Data files/O2Cell_data/',sep = "")
list_files <- list.files(path = general_path)
list_num_exp <- c(1,
                10,8,9,4,2,3,7,5,6,
                19,17,18,13,11,12,16,14,15,
                28,26,27,22,20,21,25,23,24,
                37,35,36,31,29,30,34,32,33,
                46,44,45,40,38,39,43,41,42,
                52,50,51,49,47,48,
                58,56,57,55,53,54)

list_files <- list_files[-which(list_files == "InterpretedData")]
```

# Experiment parameters

```{r }
n_exp <- length(list_files)
n_discard_start_table <- rep(150,n_exp)
n_discard_end_table <-  rep(5,n_exp)
T_test_table <-  rep(25,n_exp)
o2_sat_table <-  rep(8.35,n_exp)

# Changing value of oxygen saturation concentration data where relevant
o2_sat_table[1:28] <- 8.4*rep(1,28)
o2_sat_table[29:37] <- 8.3*rep(1,9)
o2_sat_table[53:58] <- 8.4*rep(1,6)

```


# Results analysis
```{r}
results_O2cell <- data.frame(listFiles = list_files , listNumExp = list_num_exp)
results_O2cell <- results_O2cell[order(results_O2cell$listNumExp),]


results_O2cell$lightIntensity1 <- rep(NA,n_exp)
results_O2cell$productivity1 <- rep(NA,n_exp)
results_O2cell$productivitySE1 <- rep(NA,n_exp)
results_O2cell$nLight1 <- rep(NA,n_exp)
results_O2cell$r2Light1 <- rep(NA,n_exp)
results_O2cell$pvalueLight1 <- rep(NA,n_exp)
results_O2cell$respiration1 <- rep(NA,n_exp)
results_O2cell$respirationSE1 <- rep(NA,n_exp)
results_O2cell$nDark1 <- rep(NA,n_exp)
results_O2cell$r2Dark1 <- rep(NA,n_exp)
results_O2cell$pvalueDark1 <- rep(NA,n_exp)

results_O2cell$lightIntensity2 <- rep(NA,n_exp)
results_O2cell$productivity2 <- rep(NA,n_exp)
results_O2cell$productivitySE2 <- rep(NA,n_exp)
results_O2cell$nLight2 <- rep(NA,n_exp)
results_O2cell$r2Light2 <- rep(NA,n_exp)
results_O2cell$pvalueLight2 <- rep(NA,n_exp)
results_O2cell$respiration2 <- rep(NA,n_exp)
results_O2cell$respirationSE2 <- rep(NA,n_exp)
results_O2cell$nDark2 <- rep(NA,n_exp)
results_O2cell$r2Dark2 <- rep(NA,n_exp)
results_O2cell$pvalueDark2 <- rep(NA,n_exp)


for (iexp in (1:n_exp)){
  path <- paste(general_path,results_O2cell$listFiles[iexp],sep = "")
  n_discard_start <- n_discard_start_table[iexp]
  n_discard_end <-n_discard_end_table[iexp]
  T_test <- T_test_table[iexp]
  o2_sat <- o2_sat_table[iexp]
  
  data_set <- read.csv(path, header=TRUE)
  
  results_O2cell_local <- o2cell_prod_fun_kl_corrected(data_set, paste("exp_",iexp,sep = ""), n_discard_start,
  n_discard_end,T_test,o2_sat)
  
  results_O2cell$lightIntensity1[iexp] <- results_O2cell_local$light_intensity[1]
  results_O2cell$productivity1[iexp] <- results_O2cell_local$productivity[1]
  results_O2cell$productivitySE1[iexp] <- results_O2cell_local$productivity_standardError[1]
  results_O2cell$nLight1[iexp] <- results_O2cell_local$N_light[1]
  results_O2cell$r2Light1[iexp] <- results_O2cell_local$R2_light[1]
  results_O2cell$pvalueLight1[iexp] <- results_O2cell_local$pValue_light[1]
  results_O2cell$respiration1[iexp] <- results_O2cell_local$respiration[1]
  results_O2cell$respirationSE1[iexp] <- results_O2cell_local$respiration_standardError[1]
  results_O2cell$nDark1[iexp] <- results_O2cell_local$N_dark[1]
  results_O2cell$r2Dark1[iexp] <- results_O2cell_local$R2_dark[1]
  results_O2cell$pvalueDark1[iexp] <- results_O2cell_local$pValue_dark[1]
  
  results_O2cell$lightIntensity2[iexp] <- results_O2cell_local$light_intensity[2]
  results_O2cell$productivity2[iexp] <- results_O2cell_local$productivity[2]
  results_O2cell$productivitySE2[iexp] <- results_O2cell_local$productivity_standardError[2]
  results_O2cell$nLight2[iexp] <- results_O2cell_local$N_light[2]
  results_O2cell$r2Light2[iexp] <- results_O2cell_local$R2_light[2]
  results_O2cell$pvalueLight2[iexp] <- results_O2cell_local$pValue_light[2]
  results_O2cell$respiration2[iexp] <- results_O2cell_local$respiration[2]
  results_O2cell$respirationSE2[iexp] <- results_O2cell_local$respiration_standardError[2]
  results_O2cell$nDark2[iexp] <- results_O2cell_local$N_dark[2]
  results_O2cell$r2Dark2[iexp] <- results_O2cell_local$R2_dark[2]
  results_O2cell$pvalueDark2[iexp] <- results_O2cell_local$pValue_dark[2]
}



```

## Readjusting for experiments with poorer fits
```{r, echo=TRUE}
# Changing for the run of light 1
i_exp_rerun_light1 <- c(2,3,20,21,26,28,29,32,36,39,41,45,46,47,52,53)
n_discard_start_rerun_light1 <- c(50,215,200,150,165,200,150,175,150,120,175,170,170,200,150,170) 
n_discard_end_rerun_light1 <-  c(100,5,5,10,5,5,25,15,45,50,5,5,5,5,55,5)


matrix(c(i_exp_rerun_light1,n_discard_start_rerun_light1,n_discard_end_rerun_light1),ncol = 3)

for (iexp in (1:length(i_exp_rerun_light1))){
  path <- paste(general_path,results_O2cell$listFiles[i_exp_rerun_light1[iexp]],sep = "")
  n_discard_start <- n_discard_start_rerun_light1[iexp]
  n_discard_end <-n_discard_end_rerun_light1[iexp]
  T_test <- T_test_table[i_exp_rerun_light1[iexp]]
  o2_sat <- o2_sat_table[i_exp_rerun_light1[iexp]]
  
  data_set <- read.csv(path, header=TRUE)
  
  results_O2cell_local <- o2cell_prod_fun_kl_corrected(data_set, paste("exp_",iexp,sep = ""), n_discard_start,
  n_discard_end,T_test,o2_sat)
  
  results_O2cell$lightIntensity1[i_exp_rerun_light1[iexp]] <- results_O2cell_local$light_intensity[1]
  results_O2cell$productivity1[i_exp_rerun_light1[iexp]] <- results_O2cell_local$productivity[1]
  results_O2cell$productivitySE1[i_exp_rerun_light1[iexp]] <- results_O2cell_local$productivity_standardError[1]
  results_O2cell$nLight1[i_exp_rerun_light1[iexp]] <- results_O2cell_local$N_light[1]
  results_O2cell$r2Light1[i_exp_rerun_light1[iexp]] <- results_O2cell_local$R2_light[1]
  results_O2cell$pvalueLight1[i_exp_rerun_light1[iexp]] <- results_O2cell_local$pValue_light[1]
}

```



```{r, echo=TRUE}
# Changing for the run of Resp 1
i_exp_rerun_resp1 <- c(1,11,27,29,41,44,45,46,47,53)
n_discard_start_rerun_resp1 <- c(200,200,170,75,250,50,180,185,250,250) 
n_discard_end_rerun_resp1 <-  c(5,5,5,75,5,50,15,5,10,5)

matrix(c(i_exp_rerun_resp1,n_discard_start_rerun_resp1,n_discard_end_rerun_resp1),ncol = 3)

for (iexp in (1:length(i_exp_rerun_resp1))){
  path <- paste(general_path,results_O2cell$listFiles[i_exp_rerun_resp1[iexp]],sep = "")
  n_discard_start <- n_discard_start_rerun_resp1[iexp]
  n_discard_end <-n_discard_end_rerun_resp1[iexp]
  T_test <- T_test_table[i_exp_rerun_resp1[iexp]]
  o2_sat <- o2_sat_table[i_exp_rerun_resp1[iexp]]
  
  data_set <- read.csv(path, header=TRUE)
  
  results_O2cell_local <- o2cell_prod_fun_kl_corrected(data_set, paste("exp_",iexp,sep = ""), n_discard_start,
  n_discard_end,T_test,o2_sat)
  
  results_O2cell$respiration1[i_exp_rerun_resp1[iexp]] <- results_O2cell_local$respiration[1]
  results_O2cell$respirationSE1[i_exp_rerun_resp1[iexp]] <- results_O2cell_local$respiration_standardError[1]
  results_O2cell$nDark1[i_exp_rerun_resp1[iexp]] <- results_O2cell_local$N_dark[1]
  results_O2cell$r2Dark1[i_exp_rerun_resp1[iexp]] <- results_O2cell_local$R2_dark[1]
  results_O2cell$pvalueDark1[i_exp_rerun_resp1[iexp]] <- results_O2cell_local$pValue_dark[1]
}


```

```{r, echo=TRUE}
# Changing for the run of light 2
i_exp_rerun_light2 <- c(2,3,6,11,12,18,20,24,33,38,41,42,46,52,54,56)
n_discard_start_rerun_light2 <- c(200,200,200,220,150,200,230,170,200,200,200,150,200,170,50,200) 
n_discard_end_rerun_light2 <-  c(5,5,5,5,35,5,5,5,5,5,55,55,20,25,5,5)


matrix(c(i_exp_rerun_light2,n_discard_start_rerun_light2,n_discard_end_rerun_light2),ncol = 3)


for (iexp in (1:length(i_exp_rerun_light2))){
  path <- paste(general_path,results_O2cell$listFiles[i_exp_rerun_light2[iexp]],sep = "")
  n_discard_start <- n_discard_start_rerun_light2[iexp]
  n_discard_end <-n_discard_end_rerun_light2[iexp]
  T_test <- T_test_table[i_exp_rerun_light2[iexp]]
  o2_sat <- o2_sat_table[i_exp_rerun_light2[iexp]]
  
  data_set <- read.csv(path, header=TRUE)
  
  results_O2cell_local <- o2cell_prod_fun_kl_corrected(data_set, paste("exp_",iexp,sep = ""), n_discard_start,
  n_discard_end,T_test,o2_sat)
  
  results_O2cell$lightIntensity2[i_exp_rerun_light2[iexp]] <- results_O2cell_local$light_intensity[2]
  results_O2cell$productivity2[i_exp_rerun_light2[iexp]] <- results_O2cell_local$productivity[2]
  results_O2cell$productivitySE2[i_exp_rerun_light2[iexp]] <- results_O2cell_local$productivity_standardError[2]
  results_O2cell$nLight2[i_exp_rerun_light2[iexp]] <- results_O2cell_local$N_light[2]
  results_O2cell$r2Light2[i_exp_rerun_light2[iexp]] <- results_O2cell_local$R2_light[2]
  results_O2cell$pvalueLight2[i_exp_rerun_light2[iexp]] <- results_O2cell_local$pValue_light[2]
}

```


```{r, echo=TRUE}
# Changing for the run of Resp 2
i_exp_rerun_resp2 <- c(34,46,48,54)
n_discard_start_rerun_resp2 <- c(160,190,100,200) 
n_discard_end_rerun_resp2 <-  c(15,5,10,5)


matrix(c(i_exp_rerun_resp2,n_discard_start_rerun_resp2,n_discard_end_rerun_resp2),ncol = 3)

for (iexp in (1:length(i_exp_rerun_resp2))){
  path <- paste(general_path,results_O2cell$listFiles[i_exp_rerun_resp2[iexp]],sep = "")
  n_discard_start <- n_discard_start_rerun_resp2[iexp]
  n_discard_end <-n_discard_end_rerun_resp2[iexp]
  T_test <- T_test_table[i_exp_rerun_resp2[iexp]]
  o2_sat <- o2_sat_table[i_exp_rerun_resp2[iexp]]
  
  data_set <- read.csv(path, header=TRUE)
  
  results_O2cell_local <- o2cell_prod_fun_kl_corrected(data_set, paste("exp_",iexp,sep = ""), n_discard_start,
  n_discard_end,T_test,o2_sat)
  
  results_O2cell$respiration2[i_exp_rerun_resp2[iexp]] <- results_O2cell_local$respiration[2]
  results_O2cell$respirationSE2[i_exp_rerun_resp2[iexp]] <- results_O2cell_local$respiration_standardError[2]
  results_O2cell$nDark2[i_exp_rerun_resp2[iexp]] <- results_O2cell_local$N_dark[2]
  results_O2cell$r2Dark2[i_exp_rerun_resp2[iexp]] <- results_O2cell_local$R2_dark[2]
  results_O2cell$pvalueDark2[i_exp_rerun_resp2[iexp]] <- results_O2cell_local$pValue_dark[2]
}

```
## Cas particulier :  experiment36

```{r}

iexp <- 36

path <- paste(general_path,results_O2cell$listFiles[iexp],sep = "")
n_discard_start <- 50
n_discard_end <- 50
T_test <- T_test_table[iexp]
o2_sat <- o2_sat_table[iexp]

data_set <- read.csv(path, header=TRUE)

results_O2cell_local <- o2cell_prod_fun_kl_corrected(data_set, paste("exp_",iexp,sep = ""), n_discard_start,
n_discard_end,T_test,o2_sat)

results_O2cell$lightIntensity2[iexp] <- results_O2cell_local$light_intensity[3]
results_O2cell$productivity2[iexp] <- results_O2cell_local$productivity[3]
results_O2cell$productivitySE2[iexp] <- results_O2cell_local$productivity_standardError[3]
results_O2cell$nLight2[iexp] <- results_O2cell_local$N_light[3]
results_O2cell$r2Light2[iexp] <- results_O2cell_local$R2_light[3]
results_O2cell$pvalueLight2[iexp] <- results_O2cell_local$pValue_light[3]


```

```{r}
write.csv(results_O2cell,file = paste(general_path,"/InterpretedData/24_09_11_lustulia_O2cell_results.csv",sep = ""))
```
